A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-09-16 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
switching branch

\textit{Stochastic Assumptions}
To simplify the model we make stochastic assumptions for exogenous processes.

@@

\textit{Ticket distribution} Assumptions
Model Assumptions

@@

\section{Results}
\begin{itemize}
\item Emergence of steady state behavior
\item Effects of Node failures on group and signature characteristics
\item Effects of stake distributions on group and signature characteristics
\item Additional analyses?
\end{itemize}

>>>>

\textit{Stochastic Assumptions}

To simplify the model we make stochastic assumptions for exogenous processes.

@@

\textit{Stake distribution}

Since one of our research questions involves understanding the effects of centralization
on system behavior, we use three different token distribution models with 
varying degrees of decentraliation to evaluate this impact.

\begin{itemize}
\item Linear Distribution: We assume a simple linear distribution as our most 
decentralized case. We take 50000 stakes and allocate them linearly to 100 nodes
as shown in Figure \ref{fig:linear_distribution}

\begin{figure}
    \includegraphics[width=\linewidth]{linear.png}
    \caption{Linear Stage Distribution}
    \label{fig:linear_distribution}
\end{figure}

\item Ethereum Distribution: In the spectrum of decentralization, we assume 
ETH to be moderateley decentralized. We therefore take the distribution of the 
top 30 percent account holders and apply it with some normalization in Figure \ref{fig:eth_distribution}.
(NEED TO JUSTIFY TOP 30 PERCENT)

\begin{figure}
    \includegraphics[width=\linewidth]{eth_distribution.png}
    \caption{Top 30 Percent Ethereum Distribution}
    \label{fig:eth_distribution}
\end{figure}

\item Assumed Stake Distribution: Should we disclose?
\end{itemize}

Assumptions
Model Assumptions

@@

\section{Results}
\subsection{Emergence of steady state behavior}
Using the single run experiment, we discover that steady state behavior
begins at around 400 blocks. This appears due to the smoothening out of bootstrapping
effects. (NEED TO CHECK SIM AS STEADY STATE SEEMS TO BE IN FLUX)

\begin{figure}
    \includegraphics[width=\linewidth]{steady_state.png}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
\end{figure}

\subsection{Convergence pressures}
The model primarily converges to steady state due to factors such as
signature request frequency, node availability, group creation/expiration

\subsection{Effects of Node failures on group and signature characteristics}

\begin{itemize}
    \item Effects of stake distributions on group and signature characteristics
    \item Additional analyses?
\end{itemize}
